### 2023-09-08 main.tex
fixed fixed
W-steady-proof

\end{itemize}
where
\begin{align}
	&f(x,y)=\frac{(x+y)(x-y-1)}{(x-y)(1+x+y)}&f_{1}(x,y)=\frac{(x+y)}{(x-y)(1+x+y)}\quad&f_{2}(x,y)=\frac{1}{(1+x+y)}\nonumber\\&h(x,y)=\frac{(1+x-y)(x+y+2)}{(x-y)(1+x+y)}
	&h_{1}(x,y)=-\frac{(x+y+2)}{(x-y)(1+x+y)}\quad&h_{2}(x,y)=\frac{(2+x-y)}{(x-y)(1+x+y)}\nonumber
	\\&h_{3}(x,y)=\frac{2}{(x-y)(1+x+y)}
\end{align}
\subsection{Charges}
Then we have
\begin{equation}
	\begin{split}
		T^{\Delta}(x)=tr_{0}&\left(\begin{pmatrix}
			-x&0&0&\ldots&0&(N+2x)(\alpha_{1}-\beta_{1})\\
			0&-x&0&\ldots&0&(N+2x)(\alpha_{2}-\beta_{2})\\
			\vdots&\vdots&\ddots&\vdots&\vdots&\vdots\\
			0&0&0&\ldots&-x&(N+2x)(\alpha_{N-1}-\beta_{N-1})\\
			0&0&0&\ldots&0&1+x
		\end{pmatrix}\right.
		\\& \left.
		\;\;\;\begin{pmatrix}
			D_{1,1}(x)&D_{1,2}(x)&\ldots&D_{1,N-1}(x)&C_{1}(x)\\
			D_{2,1}(x)&D_{2,2}(x)&\ldots&D_{2,N-1}(x)&C_{2}(x)\\
			\vdots&\vdots&\ddots&\vdots&\vdots\\
			D_{N-1,1}&D_{N-1,2}&\ldots&D_{N-1,N-1}(x)&C_{N-1}\\
			B_{1}(x)&B_{2}(x)&\ldots&B_{N-1}(x)&D_{N,N}(x)
		\end{pmatrix}\right)
	\end{split}
\end{equation}
Therefore we can write the polynomial expansion
\begin{equation}
	\begin{split}
		T^{\Delta}(x)=&
		(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)+\sum_{i=1}^{N-1}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)=
		\sum_{k=0}^{2L+2}Q_{k}x^{k}
	\end{split}
\end{equation}
We call these $Q_{k}$, with $k=0,\ldots,2L+2$, the \textit{charges}. \\
We can also introduce 
\begin{equation}
	T_{0}(x)=(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)\quad\text{such that}\quad T_{\Delta}(x)=T_{0}(x)+\sum_{i=2}^{N}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)
\end{equation}For large $x$, we compute them by expanding $U_{0}^{d}(x)$ in a polynomial: 
\begin{equation}
	D_{N,N}(x)=\sum_{a=0}^{2L+1}D_{N,N}^{a}x^{a}\quad D_{ii}(x)=\sum_{a=0}^{2L+1}D_{ii}^{a}x^{a}\quad B_{i}(x)=\sum_{a=0}^{2L-1}B_{i}^{a}x^{a}\quad D_{i,j}(x)=\sum_{a=0}^{2L}D_{i,j}^{a}x^{a}
\end{equation}
In the following it will be clear that only the first three coefficients of the diagonal elements and only the first coefficient of the non diagonal element are needed. 
\begin{itemize}
	\item For the element $D_{N,N}(x)$: 
%The coefficients that we need are the following:
%\begin{equation}
%	D_{N,N}(x)=D_{N,N}^{2L+1}x^{2L+1}+D_{N,N}^{2L}x^{2L+1}+D_{N,N}^{2L-1}x^{2L-1}+\ldots
%\end{equation}
where 
\begin{equation}
	D_{N,N}^{2L+1}=I^{tot}
\end{equation}
\begin{equation}
	D_{N,N}^{2L}=I^{tot}+2e_{NN}^{tot}
\end{equation}
\begin{equation}
	D_{N,N}^{2L-1}	=2e_{NN}^{tot}\left(e_{NN}^{tot}+I^{tot}\right)-L
\end{equation}
%\begin{equation}
%	\begin{split}
	%	D_{N,N}^{2L-1}=3e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+2\sum_{a\neq b}e_{NN}^{[a]}e_{NN}^{[b]}
%	\end{split}
%\end{equation}
\begin{comment}
{\color{blue}ok}

@@

{\color{blue}ok?}where we used $
\sum_{i=1}^Ne_{ii}^{tot}=L$. 
\end{comment}
\item For $D_{i,i}(x)$ with arbitrary $ i\in\{1,\ldots,N-1\}$ 
%\begin{equation}
%	D_{ii}(x)=D_{ii}^{2L+1}x^{2L+1}+D_{ii}^{2L}x^{2L}+D_{ii}^{2L-1}x^{2L-1}+\ldots
%\end{equation}
%where the coefficients
\begin{equation}\label{a2lp}
	D_{ii}^{2L+1}=-I^{tot}
\end{equation}\begin{equation}\label{a2l}
	D_{ii}^{2L}=I^{tot}-2e_{ii}^{tot}
\end{equation}
\begin{equation}
	D_{ii}^{2L-1}=2Ne_{ii}^{tot}+ 2e_{NN}^{tot}-L -2\sum_{j=1}^{N-1}e_{ij}^{tot}e_{ji}^{tot}
\end{equation}
%\begin{equation}\label{a2lm1}
%	\begin{split}
	%	D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}\right)-2\sum_{a\neq b}e_{ii}^{[a]}e_{ii}^{[b]}-2\sum_{a\neq b}\sum_{j=1\,:\,j\neq i}^{N-1}e_{ij}^{[a]}e_{ji}^{[b]}\\
	%	&=e_{11}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=1}^{N-1}e_{ij}^{[a]}e_{ji}^{[b]}\\
	%	%&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}\\
		%&=2e_{11}^{tot}+2e_{ii}^{tot}-C_1
%		&=e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=1}^{N-1}e_{ij}^{[a]}e_{ji}^{[b]}\\ 
%	\end{split}
%\end{equation}

@@

@@

To prove \eqref{SteadyState-W-Good} we do some steps. 
\paragraph{Useful relations}

@@

\textbf{Proof of \eqref{BActionVoid}: } using \eqref{B-charge} we have that 
\begin{align}
	B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=&2 \left(e_{iN}^{tot}e_{NN}^{tot}-\sum_{a,b=1\,:\,a<b}^{L}\sum_{k=1}^{N}e_{kN}^{[a]}e_{jk}^{[b]}\right)|\Psi_{0}^{0}\rangle\nonumber
	\\=&
	2\left(e_{iN}^{tot}e_{NN}^{tot}-\sum_{a,b=1\,:\,a<b}^{L}e_{NN}^{[a]}e_{jN}^{[b]}\right)|\Psi_{0}^{0}\rangle\nonumber\\=&
	\sum_{x=1}^{L}2L|N,\ldots,\tau_{x}=i,\ldots,N\rangle -2\sum_{x=1}^{L}(x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle
\end{align}
where we used the fact that 
\begin{equation}
	 e_{NN}^{tot}|\Psi_{0}^{0}\rangle=L|\Psi_{0}^{0}\rangle
\end{equation}
\begin{flushright}
	$\square$
\end{flushright}
\item For all $i,j\in\{1,\ldots,N-1\}$ with $i\neq j$
\begin{equation}\label{Dij-ref}
	D_{i,j}^{2L}|\Psi_{0}^{0}\rangle=0
\end{equation}
The proof is trivial from the definition of \eqref{Dij-Charge}. 
\item For all $i,j\in\{1,\ldots,N-1\}$ with $i\neq j$ and for all $x\in\{1,\ldots,L\}$ 
\begin{equation}
	D_{i,j}^{2L}||N,\ldots,\tau_{x}=i,\ldots,N\rangle=-2|N,\ldots,\tau_{x}=j,\ldots,N\rangle
\end{equation}
The proof is trivial from \eqref{Dij-Charge}. 
\item For all $i,j\in\{1,\ldots,N-1\}$ with $i\neq j$ 
\begin{equation}\label{GoodRelation}
	D_{i,j}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=-2B_{j}^{2L-1}|\Psi_{0}^{0}\rangle
\end{equation}
\textbf{Proof of \eqref{GoodRelation}:}
\begin{align}
	D_{i,j}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle&= D_{j,i}\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle\nonumber
	\\&=
	-2e_{ji}^{tot}\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle\nonumber
	\\&=
	-4\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=j,\ldots,N\rangle\nonumber
	\\&=
	-2B_{i}|\Psi_{0}^{0}\rangle
\end{align}
\begin{flushright}
	$\square$
\end{flushright}
\item For all $k,j,i\in\{1,\ldots,N-1\}\;:\;k\neq i$
\begin{equation}\label{DijBk-different}
	D_{k,j}^{2L}B_{i}^{L}|\Psi_{0}^{0}\rangle=0
\end{equation}
The proof is trivial following the one of \eqref{GoodRelation}. 
\item For all $ \forall i\in \{1,\ldots,N-1\}$
\begin{equation}\label{Dii-ref}
	D_{i,i}^{2L}\Psi_{0}^{0}\rangle=-|\Psi_{0}^{0}\rangle
\end{equation}
\textbf{Proof of \eqref{Dii-ref}:}
\begin{align}
	D_{i,i}^{2L}|\Psi_{0}^{0}\rangle=	(2e_{ii}^{tot}-I)|\Psi_{0}^{0}\rangle=-|\Psi_{0}^{0}\rangle
\end{align}
\begin{flushright}
	$\square$
\end{flushright}
\item $Q_{0}^{2L}$ acts diagonally on the state $|\Psi_{0}^{0}\rangle$
\begin{equation}\label{Diagonal-Q-void}
	Q_{0}^{2L}|\Psi_{0}^{0}\rangle=(2L+N)(1+L)|\Psi_{0}^{0}\rangle
\end{equation}
\textbf{Proof of \eqref{Diagonal-Q-void}:}
\begin{align}
	Q_{0}^{2L}|\Psi_{0}^{0}\rangle&=\left((N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}\right)|\Psi_{0}^{0}\rangle\\&=
	\left((N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}\right)|\Psi_{0}^{0}\rangle
	\\&=
	(N-NL-2L+2(N+1)L+2L^{2})|\Psi_{0}^{0}\rangle
\end{align}
where we used the fact that 
\begin{equation}
	\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}|\Psi_{0}^{0}\rangle=0
\end{equation}
\begin{flushright}
	$\square$
\end{flushright}
\end{itemize}

\paragraph{Two indices formula}

@@

\paragraph{Generalization for arbitrary number of indices} For fixed $k_{1},\ldots,k_{N-1}\in \mathbb{N}_{0}$, \eqref{Two-Relation} and \eqref{Commutativity-Gained} allow to write 

@@

We assume that it is true for all $k_{1},\ldots,k_{N-1}\in\{1,\ldots,N-1\}$ and we aim to show that, for all $i\in\{1,\ldots,N-1\}$,  

@@

Therefore, using \eqref{veryUsefulSeries}, we obtain

@@

\paragraph{Final formula.} Therefore, we find 

@@

Using \eqref{veryUsefulSeries} and \eqref{Diagonal-Q-void} we obtain 

>>>>

\end{itemize}
where
\begin{align}
	&f(x,y)=\frac{(x+y)(x-y-1)}{(x-y)(1+x+y)}&f_{1}(x,y)=\frac{(x+y)}{(x-y)(1+x+y)}\quad&f_{2}(x,y)=\frac{1}{(1+x+y)}\nonumber\\&h(x,y)=\frac{(1+x-y)(x+y+2)}{(x-y)(1+x+y)}
	&h_{1}(x,y)=-\frac{(x+y+2)}{(x-y)(1+x+y)}\quad&h_{2}(x,y)=\frac{(2+x-y)}{(x-y)(1+x+y)}\nonumber
	\\&h_{3}(x,y)=\frac{2}{(x-y)(1+x+y)}
\end{align}
\subsection{Charges}
Then we have
\begin{equation}
	\begin{split}
		T^{\Delta}(x)=tr_{0}&\left(\begin{pmatrix}
			-x&0&0&\ldots&0&(N+2x)(\alpha_{1}-\beta_{1})\\
			0&-x&0&\ldots&0&(N+2x)(\alpha_{2}-\beta_{2})\\
			\vdots&\vdots&\ddots&\vdots&\vdots&\vdots\\
			0&0&0&\ldots&-x&(N+2x)(\alpha_{N-1}-\beta_{N-1})\\
			0&0&0&\ldots&0&1+x
		\end{pmatrix}\right.
		\\& \left.
		\;\;\;\begin{pmatrix}
			D_{1,1}(x)&D_{1,2}(x)&\ldots&D_{1,N-1}(x)&C_{1}(x)\\
			D_{2,1}(x)&D_{2,2}(x)&\ldots&D_{2,N-1}(x)&C_{2}(x)\\
			\vdots&\vdots&\ddots&\vdots&\vdots\\
			D_{N-1,1}&D_{N-1,2}&\ldots&D_{N-1,N-1}(x)&C_{N-1}\\
			B_{1}(x)&B_{2}(x)&\ldots&B_{N-1}(x)&D_{N,N}(x)
		\end{pmatrix}\right)
	\end{split}
\end{equation}
Therefore we can write the polynomial expansion
\begin{equation}
	\begin{split}
		T^{\Delta}(x)=&
		(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)+\sum_{i=1}^{N-1}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)=
		\sum_{k=0}^{2L+2}Q_{k}x^{k}
	\end{split}
\end{equation}
We call these $Q_{k}$, with $k=0,\ldots,2L+2$, the \textit{charges}. \\
We can also introduce 
\begin{equation}
	T_{0}(x)=(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)\quad\text{such that}\quad T_{\Delta}(x)=T_{0}(x)+\sum_{i=2}^{N}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)
\end{equation}For large $x$, we compute them by expanding $U_{0}^{d}(x)$ in a polynomial: 
\begin{equation}
	D_{N,N}(x)=\sum_{a=0}^{2L+1}D_{N,N}^{a}x^{a}\quad D_{ii}(x)=\sum_{a=0}^{2L+1}D_{ii}^{a}x^{a}\quad B_{i}(x)=\sum_{a=0}^{2L-1}B_{i}^{a}x^{a}\quad D_{i,j}(x)=\sum_{a=0}^{2L}D_{i,j}^{a}x^{a}
\end{equation}
In the following it will be clear that only the first three coefficients of the diagonal elements and only the first coefficient of the non diagonal element are needed. 
\begin{itemize}
	\item For the element $D_{N,N}(x)$: 
%The coefficients that we need are the following:
%\begin{equation}
%	D_{N,N}(x)=D_{N,N}^{2L+1}x^{2L+1}+D_{N,N}^{2L}x^{2L+1}+D_{N,N}^{2L-1}x^{2L-1}+\ldots
%\end{equation}
where 
\begin{equation}
	D_{N,N}^{2L+1}=I^{tot}
\end{equation}
\begin{equation}\label{DNN-charge}
	D_{N,N}^{2L}=I^{tot}+2e_{NN}^{tot}
\end{equation}
\begin{equation}
	D_{N,N}^{2L-1}	=2e_{NN}^{tot}\left(e_{NN}^{tot}+I^{tot}\right)-L
\end{equation}
%\begin{equation}
%	\begin{split}
	%	D_{N,N}^{2L-1}=3e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+2\sum_{a\neq b}e_{NN}^{[a]}e_{NN}^{[b]}
%	\end{split}
%\end{equation}
\begin{comment}
{\color{blue}ok}

@@

{\color{blue}ok?}where we used $
\sum_{i=1}^Ne_{ii}^{tot}=L$. 
\end{comment}
\item For $D_{i,i}(x)$ with arbitrary $ i\in\{1,\ldots,N-1\}$ 
%\begin{equation}
%	D_{ii}(x)=D_{ii}^{2L+1}x^{2L+1}+D_{ii}^{2L}x^{2L}+D_{ii}^{2L-1}x^{2L-1}+\ldots
%\end{equation}
%where the coefficients
\begin{equation}\label{a2lp}
	D_{ii}^{2L+1}=-I^{tot}
\end{equation}\begin{equation}\label{Dii-charge}
	D_{ii}^{2L}=I^{tot}-2e_{ii}^{tot}
\end{equation}
\begin{equation}
	D_{ii}^{2L-1}=2Ne_{ii}^{tot}+ 2e_{NN}^{tot}-L -2\sum_{j=1}^{N-1}e_{ij}^{tot}e_{ji}^{tot}
\end{equation}
%\begin{equation}\label{a2lm1}
%	\begin{split}
	%	D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}\right)-2\sum_{a\neq b}e_{ii}^{[a]}e_{ii}^{[b]}-2\sum_{a\neq b}\sum_{j=1\,:\,j\neq i}^{N-1}e_{ij}^{[a]}e_{ji}^{[b]}\\
	%	&=e_{11}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=1}^{N-1}e_{ij}^{[a]}e_{ji}^{[b]}\\
	%	%&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}\\
		%&=2e_{11}^{tot}+2e_{ii}^{tot}-C_1
%		&=e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=1}^{N-1}e_{ij}^{[a]}e_{ji}^{[b]}\\ 
%	\end{split}
%\end{equation}

@@

\begin{equation}\label{Vacuum-state}

@@

\textbf{Remark}: relation \eqref{SteadyState-W-Good} holds only for the action of $W$ on the vacuum state $|\Psi_{0}^{0}\rangle$. Acting on different equilibrium eigenstates, exchange relations between $B_{i}^{2L-1}$ and $Q_{0}^{2L}$ are more difficult and we cannot rewrite \eqref{W-charges-Bad} in such a simpler form. 
\subsubsection{Proof of \eqref{SteadyState-W-Good}}
To prove \eqref{SteadyState-W-Good} we do four steps. 
\paragraph{1. Useful relations}

@@

\textbf{Proof of \eqref{BActionVoid}: } using \eqref{B-charge} we have that 
\begin{align}
	B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=&2 \left(e_{iN}^{tot}e_{NN}^{tot}-\sum_{a,b=1\,:\,a<b}^{L}\sum_{k=1}^{N}e_{kN}^{[a]}e_{jk}^{[b]}\right)|\Psi_{0}^{0}\rangle\nonumber
	\\=&
	2\left(e_{iN}^{tot}e_{NN}^{tot}-\sum_{a,b=1\,:\,a<b}^{L}e_{NN}^{[a]}e_{jN}^{[b]}\right)|\Psi_{0}^{0}\rangle\nonumber\\=&
	\sum_{x=1}^{L}2L|N,\ldots,\tau_{x}=i,\ldots,N\rangle -2\sum_{x=1}^{L}(x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle
\end{align}
where we used the fact that 
\begin{equation}\label{eNN-action}
	 e_{NN}^{tot}|\Psi_{0}^{0}\rangle=L|\Psi_{0}^{0}\rangle
\end{equation}
\begin{flushright}
	$\square$
\end{flushright}
\item For all $i,j\in\{1,\ldots,N-1\}$ with $i\neq j$
\begin{equation}\label{Dij-ref}
	D_{i,j}^{2L}|\Psi_{0}^{0}\rangle=0
\end{equation}
The proof is trivial from the definition of \eqref{Dij-Charge}. 
\item For all $i,j\in\{1,\ldots,N-1\}$ with $i\neq j$ and for all $x\in\{1,\ldots,L\}$ 
\begin{equation}
	D_{i,j}^{2L}||N,\ldots,\tau_{x}=i,\ldots,N\rangle=-2|N,\ldots,\tau_{x}=j,\ldots,N\rangle
\end{equation}
The proof is trivial from \eqref{Dij-Charge}. 
\item For all $i,j\in\{1,\ldots,N-1\}$ with $i\neq j$ 
\begin{equation}\label{GoodRelation}
	D_{i,j}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=-2B_{j}^{2L-1}|\Psi_{0}^{0}\rangle
\end{equation}
\textbf{Proof of \eqref{GoodRelation}:}
\begin{align}
	D_{i,j}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle&= D_{j,i}\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle\nonumber
	\\&=
	-2e_{ji}^{tot}\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle\nonumber
	\\&=
	-4\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=j,\ldots,N\rangle\nonumber
	\\&=
	-2B_{i}|\Psi_{0}^{0}\rangle
\end{align}
\begin{flushright}
	$\square$
\end{flushright}
\item For all $k,j,i\in\{1,\ldots,N-1\}\;:\;k\neq i$
\begin{equation}\label{DijBk-different}
	D_{k,j}^{2L}B_{i}^{L}|\Psi_{0}^{0}\rangle=0
\end{equation}
The proof is trivial following the one of \eqref{GoodRelation}. 
\item For all $ \forall i\in \{1,\ldots,N-1\}$
\begin{equation}\label{Dii-ref}
	D_{i,i}^{2L}\Psi_{0}^{0}\rangle=|\Psi_{0}^{0}\rangle\qquad D_{N,N}^{2L}\Psi_{0}^{0}\rangle=(1+2L)|\Psi_{0}^{0}
\end{equation}
The proof is trivial using \eqref{Dii-charge} and \eqref{DNN-charge}. 
\item $Q_{0}^{2L}$ acts diagonally on the state $|\Psi_{0}^{0}\rangle$
\begin{equation}\label{Diagonal-Q-void}
	Q_{0}^{2L}|\Psi_{0}^{0}\rangle=(2L+N)(1+L)|\Psi_{0}^{0}\rangle
\end{equation}
\textbf{Proof of \eqref{Diagonal-Q-void}:}
\begin{align}
	Q_{0}^{2L}|\Psi_{0}^{0}\rangle&=\left((N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}\right)|\Psi_{0}^{0}\rangle\\&=
	\left((N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}\right)|\Psi_{0}^{0}\rangle
	\\&=
	(N-NL-2L+2(N+1)L+2L^{2})|\Psi_{0}^{0}\rangle
\end{align}
where we used the fact that 
\begin{equation}
	\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}|\Psi_{0}^{0}\rangle=0
\end{equation}
\begin{flushright}
	$\square$
\end{flushright}
\end{itemize}

\paragraph{2. Two indices formula}

@@

\paragraph{3. Generalization for arbitrary number of indices} For fixed $k_{1},\ldots,k_{N-1}\in \mathbb{N}_{0}$, \eqref{Two-Relation} and \eqref{Commutativity-Gained} allow to write 

@@

We assume that it is true for all $k_{1},\ldots,k_{N-1}\in\mathbb{N}$ and we aim to show that, for all $i\in\{1,\ldots,N-1\}$,  

@@

As a consequence of \eqref{veryUsefulSeries} and of \eqref{Two-Relation}, it is easy to prove that for all  $k_{1},\ldots,k_{N-1}\in\mathbb{N}$

@@

\paragraph{4. Final formula.} Using \eqref{Commutativity-Gained} and \eqref{k-times-QB} the symmetrization operator written in \eqref{W-charges-Bad} acting on the vacuum state $|\Psi_{0}^{0}\rangle$ reads, for all $k_{1},\ldots,k_{N-1}\in\mathbb{N}_{0}$
	&SYM\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)
	|\Psi_{0}^{0}\rangle
	\\=&\frac{	(k_{1}+\ldots+k_{N-1})!}{k_{1}!\cdots k_{N-1}!}	\prod_{\ell=1}^{N-1}\left(Q_{0}^{2L}B_{\ell}^{2L-1}\right)^{k_{\ell}}|\Psi_{0}^{0}\rangle
	\\=&\frac{	(k_{1}+\ldots+k_{N-1})!}{k_{1}!\cdots k_{N-1}!}\prod_{\ell=1}^{N-1}\left(B_{\ell}^{2L-1}\right)^{k_{\ell}}\prod_{j=1}^{k_{1}+\ldots+k_{N-1}}\left(Q_{0}^{2L}-2j(D_{11}^{2L}+D_{NN}^{2L})+4j(j-1)\right)|\Psi_{0}^{0}\rangle
Therefore, the action of the matrix $W$ on $|\Psi_{0}^{0}\rangle$ is given by
\begin{equation}\label{intermediate-W-ss}

@@

Using \eqref{veryUsefulSeries} and observing that  we have that $2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)$ is diagonal we have that, for all $j\in{1,\ldots,k_{1}+\ldots+k_{N-1}}$ 
&\left\{(\Lambda_{0}+\epsilon)-Q_{0}^{2L}+2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle|_{\epsilon=0}\\=&
\sum_{t=0}^{\infty}\left\{2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-t}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-t-1}|\Psi_{0}^{0}\rangle
We observe that
	\lim_{\epsilon\to 0}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}\Psi_{0}^{0}=|\Psi_{0}^{0}\rangle
therefore, re-summing the series we obtain
	&\lim_{\epsilon\to 0}\left\{(\Lambda_{0}+\epsilon)-Q_{0}^{2L}+2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle|_{\epsilon=0}
	\lim_{\epsilon\to 0}\sum_{t=0}^{\infty}\left\{Q_{0}^{2L}-2j(D_{1,1}^{2L}+D_{N,N}^{2L})+4j(j-1)\right\}^{-t}\left(\Lambda_{0}+\epsilon\right)^{-t-1}\Psi_{0}^{0}
	\lim_{\epsilon\to 0}\left\{\Lambda_{0}+\epsilon-\Lambda_{0}+2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle
	\left\{2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle
Using \eqref{Dii-ref} we have 
	&\left\{2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle
	\\=&\left\{2j(2L+2)-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle
	\frac{1}{4j}\left\{L-j+2\right\}^{-1}|\Psi_{0}^{0}\rangle
Using the Euler $\Gamma$-function we have 
\prod_{j=1}^{k_{1}+\ldots+k_{N-1}}\frac{1}{2j}\left\{L-j+2\right\}^{-1}|\Psi_{0}^{0}\rangle=\frac{1}{4^{k_{1}+\ldots+k_{N-1}}}\frac{1}{(k_{1}+\ldots+k_{N-1})!}\frac{\Gamma(L+2-(k_{1}+\ldots+k_{N-1}))}{\Gamma(L+2)}|\Psi_{0}^{0}\rangle
Finally, replacing this formula in \eqref{intermediate-W-ss} and using \eqref{eNN-action} we obtain \eqref{SteadyState-W-Good}. 
%		|\Psi^{''}\rangle=&	\;W|\Psi_{0}^{0}\rangle =\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}\frac{\Delta_{1}^{k_{1}}\cdots \Delta_{N-1}^{k_{N-1}}}{k_{1}!\cdots k_{N-1}!}\\&
%		\left(\frac{B_{1}^{2L-1}}{2^{k_{1}}}\right)^{k_{1}}\cdots\left( \frac{B_{N-1}^{2L-1}}{2^{k_{N-1}}}\right)^{k_{N-1}}\frac{\Gamma\left(e_{NN}^{tot}+2-(k_{1}+\ldots+k_{N-1})\right)}{\Gamma\left(e_{NN}^{tot}+2\right)}|\Psi_{0}^{0}\rangle
